---
title: "simpleRegress"
author: "Alondra Garcia"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted R-square for this model (NECK) is 0.7476

## now predict the length of a bear who has a neck of 17, 22 and 26

```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```

The predict length of a Bear that measures 17 is 52, a Bear that measures 22 is 60 and a bear that measures 26 is 67. 

## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

```{r}
chesty <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(chesty)
summary.lm(chesty)
```

The adjusted R-square for this model (CHEST) is 0.79; The model for NECK had an adjusted R-sqaure of 0.75
So far the best model is the one based on CHEST 


```{r}
new <- data.frame(CHEST=c(17,22,26))
predict(chesty,new)
predict(chesty,new,se.fit=TRUE)
```

According to the measurements of the Bears the largest R-square is CHEST with the value of 0.79 

